\documentclass{report}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{forest}
\usepackage{amsmath}
\usepackage{multicol}
\begin{document}
\include{titlepage.tex}

\section*{Task}
The development of an interpreter for a subset of \textbf{Basic Language}. 

\vspace{0.5cm}

\subsection*{Project Goals}
\begin{itemize}
	\item Process a \textbf{Basic Language} source code file. 
	\item Tokenize the source code file. 
	\item Detect syntactical error.
	\item Display appropriate error messages during runtime. 
\end{itemize}

\subsection*{Deliverable Goals}
\begin{itemize}
	\item Develop a grammar for the subset of \textbf{Basic Language} that I will be using. 
	\item Arrays for the \emph{Keywords} and \emph{Identifiers}
	\item Ability to input source code to lexer. 
	\item Output tokens scanned. 
\end{itemize}

\subsection*{Subset of the Basic Language}
The subset of basic that I want to define for the course project is going to be kept as minimal as possible to focus on the process of developing an interpreter. 
With that in mind the lowest we can go is turing complete of course. 
For this to be true the language doesn't need much. 

\begin{multicols}{2}
\begin{itemize}
	\item Recursive Operators
		\begin{itemize}
			\item \texttt{FOR...TO...NEXT}
		\end{itemize}
	\item Conditional Jumps 
		\begin{itemize}
			\item \texttt{IF...THEN...\{ELSE\}}
			\item \texttt{GOTO}
		\end{itemize}	
	\item Variables
		\begin{itemize}
			\item \texttt{LET}
		\end{itemize}
\end{itemize}
\columnbreak
\subsection*{Tokens}
\begin{itemize}
	\item LET
	\item IF 
	\item FOR 
	\item GOTO
	\item +
	\item -
	\item *
	\item /
	\item =
\end{itemize}

\end{multicols}
\subsection*{Backus Normal Form of Basic Subset}
\begin{align*}
BASIC \; PROGRAM &::=				\\ 
	&|\; EXPRESSION, EXPRESSION 		\\
	&|\; EXPRESSION				\\
	EXPRESSION &::=				\\
	&|\; LET				\\
	&|\; IF					\\
	&|\; FOR 				\\
	&|\; GOTO				\\
	&|\; IDENTIFIER\;+\;EXPRESSION		\\
	&|\; IDENTIFIER\;-\;EXPRESSION		\\
	&|\; IDENTIFIER\;*\;EXPRESSION		\\
	&|\; IDENTIFIER\;/\;EXPRESSION		\\
	LET &::=				\\
	&| IDENTIFIER = EXPRESSION		\\
	IDENTIFIER &::=				\\
	&|\; [a-zA-Z] 				\\
	&|\; [a-zA-Z],[a-zA-Z]			\\
	IF &::=					\\
	&|\; EXPRESSION\;then\;STATEMENT	\\
	&|\; EXPRESSION\;then\;STATEMENT\;else\;IF\\
	FOR &::=				\\
	&|\;EXPRESSION\;to\;EXPRESSION\;STATEMENT\;next\\
	GOTO &::=				\\
	&|\; [0-9] 				\\
	&|\; [0-9],[0-9] 			\\
\end{align*}

\end{document}
